### 2017-08-29 Paper01_EnthalpyAndCrystallization.tex
Results - alloy comp - updated bulk alloy comp with new SEM results
Method - proof read method with minor edits

\subsection{Master alloy}
The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared with an in-house induction melting furnace within boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere. Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for injection and gravity casting respectively. Bulk amorphous \MgZnCa~ rods of nominal $2.5 mm$ diameter and plates of nominal $1.2 mm$ thickness were produced by copper mold injection casting. The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to thicknesses of $3.25 mm$. All samples and targets were stored under Ar when not being examined or used.

\subsection{\acrshort{dc} magnetron sputtering}
Films were produced from an in-house \gls{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity). The power was $15W$, typical voltage of $285-325V$, nominal chamber pressure of 1 bar, substrate temperature of $25$\degree C, and Ar flow of 3.01 \acrshort{sccm}. Films were deposited directly onto to Al \acrshort{dsc} lid substrates. Depositions were for a period of 35 minutes at an estimated rate of $0.8 nm/s$.

@@

\subsection{\acrshort{eds} analysis}
Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400-N, Hitachi, Japan; Nova NanoSEM 230/450, FEI, The Netherlands). Hyper-maps were collected with an accelerating voltage of $15-20kV$, a probe current of $50 \mu A$, counts of 5000 kps or better, dead time less than 20 \%, and working distance was 10mm.

@@

Isothermal relaxation \acrshort{dsc} was preformed by heating samples at $20 K/min$ to the desired annealing temperature, holding for desired time, and Ar quenching to room temperature.

@@

\subsection{\acrshort{xrd} characterization}
Annealing \acrshort{xrd} (Empyrean, PANalytical, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed at room temperature. 
With a generator voltage $45 kV$, tube current $40 mA$, scan step size 0.0262606, and time per step of 397.29.

Dynamic \acrshort{xrd} (D8, Bruker, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed by raising temperature at a rate of $20 K/min$ and performing scans \textit{in situ}. The first scan was performed at $35$\degree C, then $75$\degree C, after which temperature was raised in $5$\degree C increments until reaching a final temperature at $185$\degree C. The $2 \theta$ scans from $31 - 60$\degree~ were completed within $1092 sec$ ($18min,~ 12sec$) to minimise the effects of recrystallisation during the experiment.
With a generator voltage $45 kV$, tube current $100 mA$, scan step size 0.02, and time per step of 134.4.

@@

\begin{table}[h]
	\centering
	\caption{\acrshort{eds} composition of bulk and film \MgZnCa~ in atomic weight percent.}
	\begin{tabular}{ c c c }
		\toprule
		\acrshort{eds} Analysis & Bulk (at\%)  & Film (at\%)  \\
		\midrule
		Mg & $64.85 \pm 3.18$ & $63.20 \pm 3.28$ \\
		Zn & $29.55 \pm 0.82$ & $30.95 \pm 0.96$ \\
		Ca & $~~ 5.60 \pm 0.17$ & $~~ 5.85 \pm 0.19$ \\ 
		\bottomrule
	\end{tabular}
	\label{tab:EDS_Composition}
\end{table}

@@

For next paper on relaxation / rejuvenation.

>>>>

\subsection{Master alloy}
The master alloy of \MgZnCa~ was produced using high-purity elements of Mg (99.85 wt\%), Zn (99.995 wt\%), and Ca (99.8 wt\%). The alloy was prepared with an in-house induction melting furnace within boron nitride coated graphite crucibles, purged with Ar (99.997 vol.\% purity) five times, and protected with a circulating Ar atmosphere. Alloy homogeneity was ensured by heating and cooling through a cycle of 700\degree C, 385\degree C, 650\degree C, 385\degree C, 650\degree C to a casting temperature of 500 \degree C and 450\degree C for injection and gravity casting respectively. Bulk amorphous \MgZnCa~ rods of nominal $2.5 mm$ diameter and plates of nominal $1.2 mm$ thickness were produced by copper mold injection casting. The $25.4 mm$ diameter targets were prepared from cylindrical copper mold gravity castings sectioned to nominal thicknesses of $3.25 mm$, and polished. All samples and targets were stored under Ar when not being examined or used.

\subsection{\acrshort{dc} magnetron sputtering}
Films were produced from an in-house \gls{dc} magnetron sputtering facility with Ar working gas (99.997 vol.\% purity). The power was $15W$, typical voltage of $285-325V$, nominal chamber pressure of 1 bar, substrate temperature of $25$\degree C, and Ar flow of 3.01 \acrshort{sccm}. Films were deposited directly onto to Al \acrshort{dsc} lid substrates. Depositions were for a period of 35 minutes at an estimated deposition rate of $0.8 nm/s$.

@@

\subsection{\acrshort{eds} analysis}
Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400-N, Hitachi, Japan; Nova NanoSEM 230/450, FEI, The Netherlands). Hyper-maps were collected with an accelerating voltage of $15-20keV$, a probe current of $50 \mu A$, spot size 4.2, counts of 5000 kps or better, dead time less than 20\%, and working distance was $5mm$.

@@

\hl{Isothermal relaxation acrshort{dsc} was preformed by heating samples at $20 K/min$ to the desired annealing temperature, holding for desired time, and Ar quenching to room temperature.}

@@

\subsection{\acrshort{xrd} characterization}
Annealing \acrshort{xrd} (Empyrean, PANalytical, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed on heat treated bulk rods and films at room temperature. 
With a generator voltage $45 kV$, tube current $40 mA$, scan step size 0.0262606, and time per step of 397.29.

Dynamic \acrshort{xrd} (D8, Bruker, Cu $K_{\alpha}$ X-ray source, $\lambda = 1.541 \angstrom$) was performed on as manufactured bulk plates and films by raising temperature at a rate of $20 K/min$ and performing scans \textit{in situ}. The first scan was performed at $35$\degree C, then $75$\degree C, after which temperature was raised in $5$\degree C increments until reaching a final temperature at $185$\degree C. The $2 \theta$ scans from $31 - 60$\degree~ were completed within $1092 sec$ ($18min,~ 12sec$) to minimise the effects of recrystallisation during the experiment.
With a generator voltage $45 kV$, tube current $100 mA$, scan step size 0.02, and time per step of 134.4.

@@

\begin{table}[h]
	\centering
	\caption{\acrshort{eds} composition of bulk and film \MgZnCa~ in atomic weight percent.}
	\begin{tabular}{ c c c }
		\toprule
		\acrshort{eds} Analysis & Bulk (at\%)  & Film (at\%)  \\
		\midrule
		Mg & $64.92 \pm 3.22$ & $63.20 \pm 3.28$ \\
		Zn & $29.55 \pm 0.84$ & $30.95 \pm 0.96$ \\
		Ca & $~~ 5.53 \pm 0.17$ & $~~ 5.85 \pm 0.19$ \\ 
		\bottomrule
	\end{tabular}
	\label{tab:EDS_Composition}
\end{table}

@@

\hl{For next paper on relaxation / rejuvenation.}
